Something about Performance, 2D Component of NEMO. (TBC)

### 2016-01-07 nemolite2d_perf.tex
nemolite2d paper: add notes column to compiler flags table

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
\caption{The compiler flags used in this work.}
\label{TABLE_compiler_flags}
\centering
\begin{tabular}{l|c}
\hline
Compiler  &  Flags \\
\hline
Gnu       & -Ofast -mtune=native -finline-limit=50000    \\
Intel     & -O3 -fast -fno-inline-factor -xHost   \\
Cray      & -O3 -O ipa5 -h wp               \\
IBM       & -O5 -qinline=auto:level=10      \\
PGI       & {\bf Jeremy to supply} \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
\caption{The compiler flags used in this work.}
\label{TABLE_compiler_flags}
\centering
\begin{tabular}{l|l|l}
\hline
Compiler  &  Flags                                    & Notes \\
\hline
Gnu       & -Ofast -mtune=native -finline-limit=50000 &   \\
Intel     & -O3 -fast -fno-inline-factor -xHost       &   \\
Cray      & -O3 -O ipa5 -h wp                         &   \\
IBM       & -O5 -qinline=auto:level=10                &   \\
PGI       & {\bf Jeremy to supply}                    &   \\
\hline
\end{tabular}
\end{table}
